Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex
Add Component - TangleID

\subsubsection{TangleID}

>>>>

\subsubsection{TangleID}
TangleID\cite{TangleID} is a self-soverign identity system based on IOTA, the goal is to establish a solution that do not require any third-party authority to verify an identity and its digital footprint. In TangleID, the digital footprint is converted into digital assets with the principle of Decentralized Identifiers (DIDs) defined by W3C, and by putting DID documents on MAM makes TangleID a GDPR-Complianced system. Each identity has a public/private key pair recorded on MAM, it is used in digital signature for identity authentication. With every participant in data marketplace registers on TangleID, one can easily verify data provider's identity and data integrity with the public key on the DID document, and that we can ensure the reliability of data sources.
